Functional trait data tell new story about biodiversity change

### 2021-03-10 paper/manuscript.Rmd
Fix citation.

Functional diversity sheds further light on critical ecosystem and
community processes potentially impacted by anthropogenic change. For
example, there is increasing evidence that functional diversity is a
better predictor of ecosystem function than species-based metrics
[@cadotte2011; @gagic2015], and that different facets of functional
diversity also play a role in maintaining ecosystem stability
[\@craven2018; @morin2014]. Further, biogeographic assessments of
functional diversity give foundational insight into how community
assembly plays out across systems at a standardized scale [@violle2014;
@weiher2011].

@@

***Null Models***

>>>>

Functional diversity sheds further light on critical ecosystem and
community processes potentially impacted by anthropogenic change. For
example, there is increasing evidence that functional diversity is a
better predictor of ecosystem function than species-based metrics
[@cadotte2011; @gagic2015], and that different facets of functional
diversity also play a role in maintaining ecosystem stability
[@craven2018; @morin2014]. Further, biogeographic assessments of
functional diversity give foundational insight into how community
assembly plays out across systems at a standardized scale [@violle2014;
@weiher2011].

@@

#### ***Null Models***
